Reproducible Research - Peer Assignment 1 
========================================================

```{r simulation, echo=FALSE, results='hide'}
library(ggplot2)
library(gam)
library(data.table)
```

Given below are the steps undertaken for completion of peer assignment 1:

Step 1: Load the data

```{r}
setwd("C:/Sriraman/B D/5 Reproducible Research/Week 2/repdata-data-activity")
act <- read.csv("activity.csv",header=TRUE)
```

Step 2: Finding out the mean total number of steps taken per day

Histogram of total number of steps taken per day:

```{r,  results='hide'}
aggr <- aggregate(steps~date, sum, data=act)
```
```{r, fig.width=10}
ggplot(aggr,aes(x=date,y=steps))+geom_bar(stat='identity')+ theme(axis.text.x=element_text(angle=-90))
```

Step 3: Calculate and report the mean total number of steps taken per day

Following table shows the mean total number of steps taken per day or all days having valid values.

```{r}
meanact <- aggregate(steps~date, mean, data=act, na.rm=TRUE)
meanact
```

Step 4: Time series plot of interval vs average number of steps

```{r}
tsplot <- aggregate(steps~interval, mean, data=act, na.rm=TRUE)
ggplot( data = tsplot, aes( interval, steps )) + geom_line() 
```

Observation: 
============
It is observed that there is a spike in the number of steps for the duration of around 550.

Step 5: Number of missing values in the dataset

```{r}
sum(is.na(act))
```

Step 6: Replace missing values for steps with the mean of the non-missings using the na.gam.replace function. 

The new dataset is act2. The count of missing values in the new data frame is observed to be 0.

```{r}
act2 <- na.gam.replace(act)
sum(is.na(act2))
```

Step 7: Histogram of total number of steps taken per day using the new data frame:

```{r,  results='hide'}
aggrnew <- aggregate(steps~date, sum, data=act2)
```
```{r, fig.width=10}
ggplot(aggrnew,aes(x=date,y=steps))+geom_bar(stat='identity')+ theme(axis.text.x=element_text(angle=-90))
```

Observation: 
============
It is observed that the number of observations plotted on the histogram has increased. 

Step 8: Adding the Weekday Column.

```{r}
act3 <- act2
act3$wkdy <- weekdays(as.Date(act3$date))
act4 <- data.table(act3)
act4[, WkDay := ifelse(wkdy %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"), "Weekday",
                      ifelse(wkdy %in% c("Saturday", "Sunday"), "Weekend",
                              NA))]
```

Step 9: Plot of Weekday vs Weekend

```{r}
ggplot( data = act4, aes( interval, steps )) + geom_line() +  facet_wrap(~ WkDay, nrow=2, ncol=1) 
```
