Reproducible Research - Peer Assignment 1 
========================================================

```{r simulation, echo=FALSE, results='hide'}
library(ggplot2)
```

Given below are the steps undertaken for completion of peer assignment 1:

Step 1: Load the data

```{r}
setwd("C:/Sriraman/B D/5 Reproducible Research/Week 2/repdata-data-activity")
act <- read.csv("activity.csv",header=TRUE)
```

Step 2: Finding out the mean total number of steps taken per day

Histogram of total number of steps taken per day:

```{r,  results='hide'}
aggr <- aggregate(steps~date, sum, data=act)
```
```{r, fig.width=10}
ggplot(aggr,aes(x=date,y=steps))+geom_bar(stat='identity')+ theme(axis.text.x=element_text(angle=-90))
```

Step 3: Calculate and report the mean total number of steps taken per day

Following table shows the mean total number of steps taken per day or all days having valid values.

```{r}
meanact <- aggregate(steps~date, mean, data=act, na.rm=TRUE)
meanact
```

Step 4: Time series plot of interval vs average number of steps

```{r}
tsplot <- aggregate(steps~interval, mean, data=act, na.rm=TRUE)
ggplot( data = tsplot, aes( interval, steps )) + geom_line() 
```
